\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-05-24 paper/jitp_rr_memo/jitp_rr_memo.tex
adding note of the tutorial

	\item \emph{ Also, in the conclusion can you give some more examples of other research areas and questions where this approach will be useful? I think that would increase the usage and citations. Along similar lines, I hope you plan to produce step-by-step replication code and instructions about how readers can use your workflow.  I think that too will increase the usage and citations of your approach.  }

@@

@@

>>>>

	\item \emph{ Also, in the conclusion can you give some more examples of other research areas and questions where this approach will be useful? I think that would increase the usage and citations.  }

@@

	\item \emph{ Along similar lines, I hope you plan to produce step-by-step replication code and instructions about how readers can use your workflow.  I think that too will increase the usage and citations of your approach.  }

	\textbf{Response}: We will make three categories of online materials available to help readers/users effectively apply the methods workflow we develop. First, we will post a conventional replication archive to Dataverse. The replication archive will include all of our code and data. Second, the \texttt{gov2text} package is available on GitHub. Third, we have posted an interactive tutorial on Google Colab that demonstrates the key steps in the application of our pipeline using the \texttt{gov2text} package.

@@

\textbf{Response}: Fixed.

### 2021-05-24 paper/manuscript_jitp_rr.tex
adding note of the tutorial

A local government's website is an important source of information about policy priorities,  procedures, and debates. Existing research on government websites has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis. In this research note, we propose that the automated collection of website content from large samples of government websites can can compliment more targeted manual methods, and offer contributions through comparative analyses.  We also provide software to ease the use of this data collection method. In our application, we collect a new and innovative dataset---the websites of over two hundred municipal governments in the United States---to study how website content is associated with mayoral partisanship. Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.

@@

After preprocessing, our corpus consists of 356,911 documents.  In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data. The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}.

>>>>

A local government's website is an important source of information about policy priorities,  procedures, and debates. Existing research on government websites has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis. In this research note, we propose that the automated collection of website content from large samples of government websites can compliment more targeted manual methods, and offer contributions through comparative analyses.  We also provide software to ease the use of this data collection method. In our application, we collect a new and innovative dataset---the websites of over two hundred municipal governments in the United States---to study how website content is associated with mayoral partisanship. Using topic modeling methods, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity, and fire safety.

@@

After preprocessing, our corpus consists of 356,911 documents.  In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data. The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}. The package is hosted on GitHub at ({\em blinded for anonymity}). We have also created an interactive tutorial, hosted on Google Colab \citep{bisong2019google}, in which we illustrate the use of \texttt{gov2text}.
